---
title: "Understanding Moves Toward Immigration Populism"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(rstanarm)

# Consider someone whose att_end at the end of the experiment is 1 or more units
# greater than their att_start. They become more conservative on immigration
# issues. Consider such people to have made a meaningful move toward immigration
# populism. Let's use `move_to_pop` as a new variable, defined as TRUE for such
# people. We are interested to see if two variables might be associated with
# move_to_pop: treatment and age.

x <- trains %>% 
  mutate(move_to_pop = ifelse(att_end >= att_start + 1, TRUE, FALSE)) %>% 
  select(move_to_pop, treatment, age)
```


What is the causal effect of the treatment on the probability of becoming more populist? 
-Wisdom bullets 
The first question is, what population do we care about? 

What population are we imagining, and what population are we using to try and answer this question about? (MA, train station, 2012)
Is the sample over or under represented? 
Station is in MA which is a liberal state

-Fit a model to answer this question
We have three parameters: treatment, control, and error (outside of the model)


```{r fit}

# the thing we get asked about / "whats going to happen about this? is on the left side of formula (in this case, move_to_pop) // 

fit_1 <- stan_glm(data = x,
                  formula = move_to_pop ~ treatment,
                  family = binomial,
                  refresh = 0,
                  seed = 65)
```


```{r pe}

# if someone is asking me a question about one individual or a small group, im using posterior_predict. Anything else, posterior_epred

newobs <- tibble(treatment = c("Treated", "Control"))

pe <- posterior_epred(fit_1, 
                      newdata = newobs) %>% 
  as_tibble() %>%
  mutate(ate = `1` - `2`)

# we use mutate(ate) to figure out the difference between the treatment and control


```

```{r plot}

# from section 8.4 liberal ~ income section of the book 

# the number we wish we had: what number of people became more populist when exposed to the treatment? We don't have this number, so we create a posterior. 
# column 1 in our pe represents 4,000 draws from our posterior distribution (section 2.9 in the book)

pe %>% 
  ggplot(aes(x = ate)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100)  +
    labs(title = "Posterior for causal effect of treatment",
         subtitle = "Treatment makes it about 20% likely",
         x = "Difference in attitude",
         y = "Probability") +
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()

```

```{r}

# If we assign the treatment to 25 people, how many will become populist? 

# we want to repeat treatment 25 times

newobs <- tibble(treatment = c(rep("Treated", 25)))

pp <- posterior_predict(fit_1,
                  newdata = newobs) %>%
  as_tibble() %>%
  mutate_all(as.numeric) %>%
  rowwise() %>%
  mutate(total = sum(c_across())) 

  
pp %>%
  ggplot(aes(x = total)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(title = "Posterior for Number of People who Became More Populist",
       subtitle = "Ten is the most likely number, but values from 4 to 15 are plausible",
       x = "Number",
       y = "Probability") +
  scale_x_continuous(labels = scales::number_format(1)) +
  scale_y_continuous(labels = scales::percent_format(1)) +
  theme_classic()




```


